---
title: "NFnetFU Dataset 3"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

Set Working Directiory :
```{r}
setwd("/Users/Vartika_Bisht/Individual_Project")
```

Load all source codes :
```{r}
source("Penalty_Function.R")
source("Incorporate_Groups.R")
source("Libraries_Needed.R")
source("Borrowed_Functions.R")
source("MicrobiomeAnalyst.R")
source("best_epsilon_DBSCAN.R")
```

Load Data Set :
```{r}
# Load Dataset 3
Data_Set_1 <- read.csv("/Users/Vartika_Bisht/NFnetFU/Data/NFnetFU_Dataset3_OTU_abundance(top 100).csv")

# Choose Microbiome Data
df_data1 <- as.data.frame(Data_Set_1[,2:101])
data1 <- data.matrix(df_data1)

# Create labels for prediction ( 2nd column )
meta <- read.csv("/Users/Vartika_Bisht/NFnetFU/Data/NFnetFU_Dataset3_metadat.csv")
label_dat <- as.numeric(factor(meta$chem_administration))

```

Input Dataset :
```{r}
head(df_data1)
```

Input Data for Module 1 (Features) :
```{r}
head(as.data.frame(data1))
```

Input Data for Module 1 (Output Variable: Given Variable) :
```{r}
#Labels
as.character(meta$chem_administration)
```

Input Data for Module 1 (Output Variable: Desired Labels) :
```{r}
#Desired Labels
label_dat
```

Module 1:
```{r}
## Input : Numeric Labels(label_dat) and Microbiome Abundance Data(data1)
source("Module_1.R")
## Output : Rule Based Matrix (rules_int) , Scaled Rule Based Matrix (scaled_rules_int) and Labels (label_dat)
```

Module 1 Output (Rule Based Matrix):
```{r}
head(as.data.frame(rules_int))
```

Module 1 Output (Labels):
```{r}
as.data.frame(label_dat)[,1]
```

Module 2:
```{r}
## Input : Scaled Rule Based Matrix (scaled_rules_int)
source("Module_2.R")
## Output : Rule Based matrix with Colinearity Handled (new_data1) and PCA Loadings used to combine groups (PCA_loadings) 
```

Module 2 Output (Clusters):
```{r}
groups_we_need
```

Module 2 Output (PCA Loadings):
```{r}
head(as.data.frame(t(PCA_loadings)))
```

Module 2 Output (New Data Frame):
```{r}
head(as.data.frame(new_data1))
```

Module 3:
```{r}
## Input : Rule Based matrix with Colinearity Handled (new_data1) and PCA Loadings used to combine groups (PCA_loadings) 
source("Module_3.R")
## Output : Feature Parameters (feature_score)
```

Module 3 Output (Adaptive LASSO Results):
```{r}
head(as.data.frame(feature_scores))
```

Performace:
```{r}
predicted_values <- predict(alasso1_cv,data_new, type = 'response',s = alasso1_cv$lambda.min)
library(PRROC)

PRROC_obj <- roc.curve(scores.class0 = predicted_values, weights.class0=label_dat,
                       curve=TRUE)
plot(PRROC_obj)
```


Module 4 (TSEA - Specify Disease):
```{r}
#Diseases to look for in TSEA
disease <- c("Colorectal","Crohn","Colon")
```

Module 4 (TSEA Type of feature):
```{r}
TSEA_feature <- "OTU"
```


Module 4 (TSEA - OTU):
If Features are OTU and need to be changed into appropriate Microbes for TSEA
```{r}
if(TSEA_feature == "OTU"){
#List of Microboes from selected features (OTU)
#OTU to Microbes
OTU_file <- read.table("/Users/Vartika_Bisht/NFnetFU/Data/NFnetFU_Dataset3_taxanomy.csv", header = 1)
OTU_index <- which(OTU_file$OTU %in% rownames(feature_scores))
selected_OTU <- OTU_file[OTU_index,]
feature_inorder <- selected_OTU$OTU
write.csv(selected_OTU,"OTU Microbes Selected Table.csv")

#Valid Microbe Names
OTU_network <- c()
taxa <- strsplit(as.character(selected_OTU$Taxonomy),";")
for(i in 1:length(taxa)){
  if(taxa[[i]][1] == "unclassified(100)"){
    OTU_network <- c(OTU_network,"unclassified")
  }else{
     for(j in rev(taxa[[i]])){
    mname <- substr( j , 1 , nchar(j)-5)
    if(mname != "unclassified"){
      OTU_network <- c(OTU_network,mname)
      break()}
    }
  }
}

Name_Change <- as.data.frame(OTU_network)
rownames(Name_Change) <- feature_inorder
write.csv(Name_Change,"Features to Microbes for TSEA.csv")

}

```

Module 4 (TSEA - Microbes of Different Taxa Level):
If Features are Microbes of Different Taxa Level and need to be changed into appropriate Microbes for TSEA
```{r}
if(TSEA_feature == "Microbes"){
  #List of Microboes from selected features (Microbes)
  #Microbes_name <- substring(colnames(rules_int),4)
  Microbes_name <- colnames(rules_int)
  OTU_network <- c()
  for(i in Microbes_name){
    n <- strsplit(i,c(";"))[[1]]
    if((length(n)>1)&&(n[1] == "uncultured")||(length(n)>1)&&(n[1] == "X")){
      if((n[2] == '1')||(n[2] == '2')){
        OTU_network <- c(OTU_network,'uncultured')
      }else{ OTU_network <- c(OTU_network,n[2])}
    }else{
      if((n[2]%in%c("02d06","PW3","SMB53","cc_115","rc4-4"))||(n[1]=="Unclassified_Genus")){
        OTU_network <- c(OTU_network,n[1])
      }else {OTU_network <- c(OTU_network,n[2])}
    }
  }
  feature_inorder <- colnames(rules_int)
  
  Name_Change <- as.data.frame(OTU_network)
  rownames(Name_Change) <- feature_inorder
  write.csv(Name_Change,"Features to Microbes for TSEA.csv")
}
```

Module 4 (TSEA - The names used for TSEA with the feature associated):
```{r}
head(as.data.frame(Name_Change))
```

Module 4 (TSEA - The names used for TSEA with the feature associated):
```{r}
Microbes <- unique(Name_Change$OTU_network)
Microbes <- as.character(Microbes)
Microbes
```

Module 4 (TSEA - The names used for TSEA with the feature associated):
```{r}
## Input : List of Microbes
source("Module_4(TSEA Network).R")
## Output : Network and Network Legends with Node size (Legends)
```

Module 4 (TSEA Network):
```{r}
plot(g, layout=layout_in_circle, vertex.size=vertex_wt,edge.width = E(g)$weight)
```

Module 4 (TSEA Network Legends):
```{r}
as.data.frame(Network_Info)
```

Module 4 (Infusing Data Driven Information):
TSEA Network and Adaptive LASSO Results
```{r}
## Input : TSEA Network and Adaptive LASSO Results
Cluster_Parameters <- c()
Cluster_OTU_name <- c()
for (i in Network_Info[,"Microbe Names"]) {
  index <- which(OTU_network %in% i)
  OTU <- as.character(feature_inorder[index])
  Cluster_OTU_name <- append(Cluster_OTU_name,list(OTU))
  if(length(OTU) > 1){
    OTUs_val <- c()
    for (j in OTU) {
      OTUs_val <- c( OTUs_val , abs(feature_scores[j,]) )
    }
    CP <- (sum(OTUs_val)/length(OTUs_val))[1]
  } else {
    CP <- abs(feature_scores[OTU,])
  }
  Cluster_Parameters <- c( Cluster_Parameters , CP )
}
Data_Bio_Driven <- cbind(Network_Info,Cluster_Parameters)
rownames(Data_Bio_Driven) <- NULL
colnames(Data_Bio_Driven)[4] <- "Node Score"
write.csv(Data_Bio_Driven,"Biological Network with Data Driven Results fused.csv")
## Output : Data Driven Cluster Parameters added

```

Module 4 (Infusing Data Driven Information):
TSEA Network and Adaptive LASSO Results
```{r}
as.data.frame(Data_Bio_Driven)
```

Module 4 (Infusing Data Driven Information):
Module 2 Clusters and TSEA Network
```{r}
## Input : Module 2 Clusters and TSEA Network
source("Module_4(Data Driven Network).R")
## Output : Network with Data Driven Clusters
```

Module 4 (Infusing Data Driven Information):
Module 2 Clusters and TSEA Network
```{r}
#Green Edges <- TSEA
#Red Edges <- Data Driven Cluslters
plot(gh, layout=layout_in_circle, vertex.size=vertex_wt_gh,edge.width = E(gh)$weight,edge.color=col_edges)
```

Module 4 (Infusing Data Driven Information):
Module 2 Clusters and TSEA Network
```{r}
as.data.frame(Data_Bio_Driven_with_clusters)
```









